Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-18 content/contribution/CoDeR.tex
finished describing the streamed data model of CoDeR in a more coherent manner.  still a few long sentences, but not as bad now :-)

	% Stream-based Data Model
	The data model of CoDeR is composed of two classes of streams.
	The first are \emph{input}/\emph{output} streams, and provide the semantics of streams $S$, $P$ and $N$ for any ${CDP}$ expressed by a CoDeR-based system;
	they are sequences of instances of RDF triples, where an instance of an RDF triple is an RDF triple annotated with the time interval for which it is valid \citep{SemanticStreamingManagement,sparkwave} according to the ${CDP}$ expressed: ${\langle (s,p,o),i_{e},i_{n} \rangle}$.
	This interval for any entailed fact instance is derived from the valid time intervals of the fact instances that justify it, as shown in \reffig{intersected-intervals}:
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.45\textwidth]{intersected-intervals}
		\caption{Derivation of valid-time for entailed fact instance from those of its justifying fact instances.}
		\labelfig{intersected-intervals}
	\end{figure}
	if ${A = \{c\,\text{:-}\,a\,,\,b\,.\}}$ and ${W^{S,3}_{2} = \{ \langle a,1,3 \rangle , \langle b,2,4 \rangle \}}$, then ${CDP_{2} = A \cup W^{S,3}_{2} \vDash \{ \langle a,1,3 \rangle , \langle b,2,4 \rangle , \langle c,2,3 \rangle \}}$, where $a$, $b$ and $c$ are RDF triples.
	It is in the base case of this derivation that the semantic window range $R$ of a ${CDP}$ is expressed:
	each fact instance arriving on an \emph{input} stream has a valid interval from the time of its arrival at the system for the duration of the semantic window expressed by that range $R$.

	Given that the ordering of instances in the \emph{output} stream by the value of $i_{e}$ yields the sequence of instances in the semantic stream $P$ entailed by a ${CDP}$, and that their ordering by the value of $i_{n}$ yields the sequence of instances in the semantic stream $N$, this gives all streams of CoDeR a dual semantics with respect to Continuous Datalog.

>>>>

	% Stream-based Data Model
	The data model of CoDeR is composed of two classes of streams.
	The first are \emph{input}/\emph{output} streams, and provide the semantics of streams $S$, $P$ and $N$ for any ${CDP}$ expressed by a CoDeR-based system;
	they are sequences of instances of RDF triples, where an instance of an RDF triple is an RDF triple annotated with the time interval for which it is valid \citep{SemanticStreamingManagement,sparkwave} according to the ${CDP}$ expressed: ${\langle (s,p,o),i_{e},i_{n} \rangle}$.
	This interval, for any entailed fact instance, is derived from the valid time intervals of the fact instances that justify it, as shown in \reffig{intersected-intervals}:
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.45\textwidth]{intersected-intervals}
		\caption{Derivation of valid-time for entailed fact instance from those of its justifying fact instances.}
		\labelfig{intersected-intervals}
	\end{figure}
	if ${A = \{c\,\text{:-}\,a\,,\,b\,.\}}$ and ${W^{S,3}_{2} = \{ \langle a,1,3 \rangle , \langle b,2,4 \rangle \}}$, then ${CDP_{2} = A \cup W^{S,3}_{2} \vDash \{ \langle a,1,3 \rangle , \langle b,2,4 \rangle , \langle c,2,3 \rangle \}}$, where $a$, $b$ and $c$ are RDF triples.
	It is in the base case of this derivation that the semantic window range $R$ of a ${CDP}$ is expressed:
	each fact instance arriving on an input stream has a valid interval from the time of its arrival at the system for a duration equal to the range $R$.

	The second class of streams the make up the CoDeR data model are \emph{inter-operator} streams, which are produced and consumed by the stream-to-stream operators of CoDeR's minimal algebra.
	These streams are sequences of the partial results of processing between one step in the production of entailments and the next.
	As the production of entailments in CoDeR is cast as a pattern matching problem, all partial results of this process will take the form of instances of RDF \emph{graphs};
	for a given inter-operator stream, each such RDF graph will match the same graph pattern, that being a sub-pattern of the body of one of the axiomatic rules $A$.
	As with instances of RDF triples, instances of RDF graphs are RDF graphs that are annotated with the time interval for which they are ``valid'': ${\langle \{(s,p,o),\dots,(s',p',o')\},i_{e},i_{n} \rangle}$.
	As these instances of RDF graphs may be considered to be ``entailed'' by the presence of valid instances of their constituent RDF triples within the system, the same semantics of validity may be applied to these partial matches as to the true entailments of the model, and their valid-time intervals may derived from their justifying instances in the same manner.
	It follows that inter-operator streams are, functionally, a general case of input/output streams, as the latter are simply sequences of instances of singleton RDF graphs matching the pattern ${\{(?s,?p,?o)\}}$.

	Given that the ordering of instances in the output stream of a CoDeR-based system by the value of $i_{e}$ yields the sequence of instances in the semantic stream $P$ entailed by a ${CDP}$, and that their ordering by the value of $i_{n}$ yields the sequence of instances in the semantic stream $N$, this gives the output streams of CoDeR a dual semantics with respect to Continuous Datalog.
	Furthermore, this dual semantics applies to all the streams of CoDeR, each expressing both the stream of entailment instances \emph{and} instance negations produced by a specific pipeline of CoDeR operators applied to some set of continuous RDF data sources.
